Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
S prefix for suppl. figures
Light pass over suppl.

@@

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and
overall eight $t$-contrast for the audio-description stimulus (Tab.~\ref{tab:av-contrasts})
by varying the contrasted categories (and thus the
amount of available data), and how well the annotated events within categories
on average matched a stimulus type that we assumed to correlate with spatial
perception.
% NeuroVault
Unthresholded z -maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

@@

% AD: results
In results of the audio-description stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap (Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Reliably across contrast of the audio-description stimulus, we find bilaterally significant
clusters also in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).
% non-systematic
Lastly, some contrasts of the audio-description stimulus yielded significant clusters in
regions that were not statistically significant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum
[border to triangularis], left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find [many] clusters
in a single contrasts or systematically across contrasts that are scattered
across the brain and hamper the interpretation of results.
% AV: null results regarding attention and eye movements
For example in the movie results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.
% AD: auditory cortices
Nevertheless, contrasts of the audio-description stimulus that compare (among others) verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
purpose)}

@@

% intro
For the purpose of negative control, we implemented five contrasts for every
stimulus.
% AV: no_cut > x
In the analysis of the movie data, none of the four contrasts that compared the
\texttt{no\_cut} category to a movie cut category (Tab.~\ref{tab:av-contrasts})
yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the movie stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).
% AD stimulus
In the analysis of the audio-description data, we created control contrasts based on events of
the annotated movie cuts (Tab.~\ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{odd imo}

\todo[inline]{why did I build contrasts of the no\_cut condition compared
to the movie cuts categories????}

>>>>

\setcounter{figure}{0}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\makeatother

@@

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and
overall eight $t$-contrast for the audio-description stimulus (Tab.~\ref{tab:av-contrasts})
by varying the contrasted categories (and thus the
amount of available data), and how well the annotated events within categories
on average matched a stimulus type that we assumed to correlate with spatial
perception.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AD: results
For the audio-description stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap (Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Reliably across contrast of the audio-description stimulus, we find bilaterally significant
clusters also in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).
% non-systematic
Lastly, some contrasts of the audio-description stimulus yielded significant clusters in
regions that were not statistically significant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum, left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

% ``confounding'' clusters
Our whole brain analysis did not identify systematically occuring clusters pointing
to confounding cognitive processes like attention or eye movements
% AV: null results regarding attention and eye movements
% AD: auditory cortices
Nevertheless, for the audio-description stimulus contrasts that compare verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across events and the employed nuisance regressors did not
capture this variance appropriately.
% possible reason
Activity in such clusters could be correlated with a possible
change of the soundscape when the narrator of the audio-description,
corresponding to a cut in the movie, switches udio-description stimulusto a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should extensively annotate the stimulus material
and test for correlations among variables.

@@

\todo[inline]{This section feels incomplete. Some explanation (attempts) are
missing.  Sometimes it is simply unclear which data were analyzed with which
designs. Maybe subheadings would help?}

@@

% intro
We implemented five contrasts for every stimulus.
% AV: no_cut > x
In the analysis of the movie data, none of the four contrasts that compared the
\texttt{no\_cut} category to a movie cut category (Tab.~\ref{tab:av-contrasts})
yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns that did not actually exist in the movie stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).\todo{explanation?}

% AD stimulus
For the analysis of the audio-description, we created control contrasts based on events of
the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although invisible
were nevertheless frequently perceivable due to changes in the soundscape.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{explanation?}
